Network Cascades

### 2016-08-26 paper/paper.tex
Remove criticality thing, Watts reference is broke
Fix introduction to be less cavemany

Since caveman times people have been wondering how the ball gets rolling.

@@

At the lower boundary of the cascade window, with $z = 1.05$, the curve resembles a power law distribution (note the logarithmic axes). This distribution is very similar to avalanches in self-organized criticality models (TODO $wat$). This distribution can be explained by most nodes being vulnerable given the low value of $z$, so cascades can spread to neighbors very easily. The constraining factor is the connectivity of the network, that is, missing connections inhibit the cascade's progressions, not a high convincability threshold of agents.

>>>>

Many phenomena in society seemingly start from nothing and propagate through people until they reach everyone. Examples include popular media, technology use, viral videos and even political activism, such as coups or protest movements: all of them usually start as an idea in the heads of few people and somehow gain popularity by spreading from person to person.

@@

At the lower boundary of the cascade window, with $z = 1.05$, the curve resembles a power law distribution (note the logarithmic axes). This distribution can be explained by most nodes being vulnerable given the low value of $z$, so cascades can spread to neighbors very easily. The constraining factor is the connectivity of the network, that is, missing connections inhibit the cascade's progressions, not a high convincability threshold of agents.
